---
title: "Crypto Rolling Efficiency"
format: 
  html:
    self-contained: true
execute: 
  echo: false

editor: visual
---

```{r}
#| echo: false
#| output: asis
#| message: false
#| results: hide
#| include: false
#| warning: false

source('trading_signals_deltaH.R')
library(knitr)
library(kableExtra)


```

# Time series Plots

## Window : 360

-   Delta H computed over rolling 360 days

-   Confidence interval obtained from 10.000 GBM simulations series of returns of length equal to 360

    ```{r}
    #| echo: false
    #| output: asis

    cat(paste("*","q70:",q70_360,"\n"))
    cat(paste("*","q90:",q90_360,"\n"))
    cat(paste("*","q95:",q95_360,"\n"))
    cat(paste("*","q99:",q99_360,"\n"))


    ```

```{r}
#| echo: false
#| output: asis



for(t in unique(deltaH_melt_360$Ticker)){
  cat(paste("###",t,"\n"))
  
  print(plot_time_varying_efficiency(deltaH_melt_360,t,'360'))
  cat("\n")
  
  
}
cat("\n")

```

## Window : 720

-   Delta H computed over rolling 720 days

-   Confidence interval obtained from 10.000 GBM simulations series of returns of length equal to 720

    ```{r}
    #| echo: false
    #| output: asis

    cat(paste("*","q70:",q70_720,"\n"))
    cat(paste("*","q90:",q90_720,"\n"))
    cat(paste("*","q95:",q95_720,"\n"))
    cat(paste("*","q99:",q99_720,"\n"))


    ```

```{r}
#| echo: false
#| output: asis



for(t in unique(deltaH_melt_720$Ticker)){
  cat(paste("###",t,"\n"))
  
  print(plot_time_varying_efficiency(deltaH_melt_720,t,'720'))
  cat("\n")
  
}
cat("\n")

```

## Window : 1080

-   Delta H computed over rolling 1080 days

-   Confidence interval obtained from 10.000 GBM simulations series of returns of length equal to 1080

    ```{r}
    #| echo: false
    #| output: asis

    cat(paste("*","q70:",q70_1080,"\n"))
    cat(paste("*","q90:",q90_1080,"\n"))
    cat(paste("*","q95:",q95_1080,"\n"))
    cat(paste("*","q99:",q99_1080,"\n"))


    ```

```{r}
#| echo: false
#| output: asis



for(t in unique(deltaH_melt_1080$Ticker)){
  cat(paste("###",t,"\n"))
  
  print(plot_time_varying_efficiency(deltaH_melt_1080,t,'1080'))
  cat("\n")
  
}
cat("\n") 

```

# Summary Tables

## Window : 360

```{r}

status_efficiency_crypto_360 |>
  kable(format = "html") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

## Window : 720

```{r}

status_efficiency_crypto_720 |>
  kable(format = "html") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

## Window : 1080

```{r}

status_efficiency_crypto_1080 |>
  kable(format = "html") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

# Backtesting

Return KPIs for various strategies applied to different cryptocurrencies:

-   Short-Inefficiency-Long-Efficiency: go short when the series becomes statistically inefficient (above a certain quantile - e.g. q90) and go long when it is below that level.

Short-Inefficiency: stay short only when the series becomes statistically inefficient and do nothing when it is below that level.

-   Short-Efficiency: stay short only when the series becomes statistically efficient and do nothing when it becomes inefficient.

-   Short-Efficiency-Long-Inefficiency: stay long only when the series becomes statistically efficient and do nothing when it becomes inefficient.

Note: Positions are taken one day after the efficiency level crosses the significance quantile.

```{r}
table_results <- list() 

```

## **360-day Window**

```{r}
#| echo: false
#| output: asis


positions <- c('Short-Inefficiency-Long-Efficiency', 'Short-Inefficiency', 'Short-Efficiency-Long-Inefficiency', 'Short-Efficiency')

quantiles_ineff <- c("q70",'q90','q95','q99')



for(q in quantiles_ineff){
  cat(paste("### Significance",q, "\n"))
  for (position in positions) {
  
  
  result <- consolidate_backtests(deltaH_melt_360, threshold_column=q, position=position)[[2]]|> 
    dplyr::arrange(desc(`Annualized Return`)) |>
    dplyr::mutate(Significance_level = q) |>
    dplyr::mutate(Window = 360)
  
  table_results[[length(table_results) + 1]] <- result 
  # Create a topic for each result
  cat(paste("*",q," : ", position, "\n"))
  
  # Print the result as a kable table with styling
  kable_result <- kable(result, format = "html") %>%
    kable_styling(bootstrap_options = "striped", full_width = FALSE)
  cat(kable_result)
  
  
}
  
}

print("\n")

```

## 720 window

```{r}
#| echo: false
#| output: asis


positions <- c('Short-Inefficiency-Long-Efficiency', 'Short-Inefficiency', 'Short-Efficiency-Long-Inefficiency', 'Short-Efficiency')

quantiles_ineff <- c("q70",'q90','q95','q99')

for(q in quantiles_ineff){
  cat(paste("### Significance",q, "\n"))
  for (position in positions) {
  
  
  result <- consolidate_backtests(deltaH_melt_720, threshold_column=q, position=position)[[2]]|> 
    dplyr::arrange(desc(`Annualized Return`)) |>
    dplyr::mutate(Significance_level = q) |>
    dplyr::mutate(Window = 720)
  table_results[[length(table_results) + 1]] <- result 
  # Create a topic for each result
  cat(paste("*",q," : ", position, "\n"))
  
  # Print the result as a kable table with styling
  kable_result <- kable(result, format = "html") %>%
    kable_styling(bootstrap_options = "striped", full_width = FALSE)
  cat(kable_result)
  
  
}
  
}

print("\n")

```

## 1080 Window

```{r}
#| echo: false
#| output: asis


positions <- c('Short-Inefficiency-Long-Efficiency', 'Short-Inefficiency', 'Short-Efficiency-Long-Inefficiency', 'Short-Efficiency')

quantiles_ineff <- c("q70",'q90','q95','q99')

for(q in quantiles_ineff){
  cat(paste("### Significance",q, "\n"))
  for (position in positions) {
  
  
  result <- consolidate_backtests(deltaH_melt_1080, threshold_column=q, position=position)[[2]] |> 
    dplyr::arrange(desc(`Annualized Return`)) |>
    dplyr::mutate(Significance_level = q) |>
    dplyr::mutate(Window = 1080)
  
  table_results[[length(table_results) + 1]] <- result 
  # Create a topic for each result
  cat(paste("*",q," : ", position, "\n"))
  
  # Print the result as a kable table with styling
  kable_result <- kable(result, format = "html") %>%
    kable_styling(bootstrap_options = "striped", full_width = FALSE)
  cat(kable_result)
  
  
}
  
}

print("\n")
```

```{r}
#| echo: false
#| output: asis
#| message: false
#| results: hide
#| include: false
#| warning: false

table_results |> 
  bind_rows() |> 
  writexl::write_xlsx("backtests_trading/kpis.xlsx")


```
